Pottery decor as networks on the Middle Niger

### 2024-05-15 analysis/paper/paper.Rmd
old changes

# import decor count per site
n_decors <- read_csv2(here::here("analysis/data/raw_data/n_decor.csv")) |> 
  rename(sites = site) |> 
  select(-1)

@@

i <- iNEXT(decors_abs, q=0, datatype="abundance")

i

 i <- decors_abs[,c(2,4,11)]|> 
 iNEXT(q=c(0,1,2), datatype="abundance")
 ggiNEXT(i, type=1, facet.var="Assemblage")

  i <- decors_abs[,c(4)]|> 
 iNEXT(q=c(0), datatype="abundance")
 ggiNEXT(i, type=1, facet.var="Assemblage")

 i <- decors_abs[,c(8,15,16)]|> 
 iNEXT(q=c(0,1,2), datatype="abundance")
  ggiNEXT(i, type=1, facet.var="Assemblage")

  i <- decors_abs[,c(8)]|> 
 iNEXT(q=c(0), datatype="abundance")
  ggiNEXT(i, type=1, facet.var="Assemblage")

    i <- decors_abs[,c(13)]|> 
 iNEXT(q=c(0), datatype="abundance")
  ggiNEXT(i, type=1, facet.var="Assemblage")

decors_abs <- decorsearly |> 
  left_join(n_decors) |> 
    mutate(across(where(is.numeric), ~ .*n/100)) |> 
  mutate(across(where(is.numeric), ~ round(.))) |> 
    column_to_rownames("sites") |> 
  select(-n) |> 
t()

iNEXT(decors_abs, q=0, datatype="abundance")
```

@@

 i <- decors_abs[,c(2,4,11)]|> 
 iNEXT(q=c(0,1,2), datatype="abundance")
 ggiNEXT(i, type=1, facet.var="Assemblage")

 i <- decors_abs[,c(8,15,16)]|> 
 iNEXT(q=c(0,1,2), datatype="abundance")
  ggiNEXT(i, type=1, facet.var="Assemblage")

@@

```
```{r}
i$DataInfo |> 
  arrange(n) |> 
  mutate_at(vars(2:14), as.numeric) |> 
  ggplot(aes(x = Assemblage))+
  geom_point(aes(y = n)) +
  geom_point(aes(x = Assemblage, y = SC))
```

@@

```{r total-network-sample, fig.cap="Partially overlapping networks of four decorative practices", echo = FALSE}
decor_graph |>
  activate(edges) |>
  # Filter "edges" based on 4 specific decorations
  filter(name %in% c("braided_cord_roulette",
                     "braided_strip_roulette",
                     "paint",
                     "straight_cord_mat")) |>

@@

```{r backbone-extraction, fig.cap="Extraction of binary backbones at decreasing significance levels: a) 0.05, b) 0.15, c) 0.18"}
# extract binary backbones at decreasing levels of significance
decor_05 <- extract_backbone(decor_flat, 0.05)
decor_15 <- extract_backbone(decor_flat, 0.15)
decor_20 <- extract_backbone(decor_flat, 0.20) #20 ideale anzahl?

>>>>

# import decor count per site
n_decors <- read_csv2(here::here("analysis/data/raw_data/n_decor.csv")) |> 
  rename(sites = site) |> 
  select(-1)
```

@@

iNEXT(decors_abs, q=0, datatype="abundance")

@@

 i <- decors_abs[,c(2,5,8)]|> 
 iNEXT(q=c(0,1,2), datatype="abundance")

@@

@@

```{r total-network-sample, fig.cap="Partially overlapping networks of four decorative practices", echo = FALSE}
decor_graph |>
  activate(edges) |>
  # Filter "edges" based on 4 specific decorations
  filter(name %in% c("braided_cord_roulette",
                     "braided_strip_roulette",
                     "paint",
                     "straight_mat_impression")) |>

@@

```{r backbone-extraction, fig.cap="Extraction of binary backbones at decreasing significance levels: a) 0.05, b) 0.15, c) 0.18"}
# extract binary backbones at decreasing levels of significance
decor_05 <- extract_backbone(decor_flat, 0.05)
decor_15 <- extract_backbone(decor_flat, 0.14)
decor_20 <- extract_backbone(decor_flat, 0.20) #20 ideale anzahl?
